{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-10 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\section{Stepwise formulation of weak accelerated proximal gradient}
    In this section, we introduce the following new quantities and their notations. 
    It's there to make the notations simpler and easier to follow for the proofs that will come later. 
    The algorithm is parameterized by the sequence $y_k, x_k$. 
    We define for all $k \ge 0$ the following quantities: 
    \begin{assumption}
        Choose any integer $k\ge 0$. 
        Given $x_k, y_k, v_k$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &= F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ always. 
    \end{assumption}

    \begin{theorem}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$. 
        Define scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}

    \end{theorem}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref*{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        With the equalities, we define the following quantities associate with it. 
        Fix any integer $k \ge 0$. 
        To verify, we use the fundamental proximal gradient inequality. 
        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.

@@

@@

\section{Formulation of WAPG and its convergence rates}

    \begin{definition}[Weak accelerated proximal gradient (WAPG)]\label{def:wapg}
        \;\\
        Choose any $\gamma_0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, they have $\rho_k \in [0, 1], \alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k - 1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \end{definition}

    \begin{proposition}[WAPG convergence claim]\label{prop:wagp-convergence}
        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by the weak accelerated proximal gradient algorithm. 

@@

        $$
        \begin{aligned}

@@

        \end{aligned}
        $$

@@

        Recall Proposition \ref{prop:stepwise-lyapunov},
        since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us: 
        {\footnotesize

@@

            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

@@

@@

        Going from the left to the right on the second inequality, we used the fact that $\rho_{k - 1} \in [0, 1]$. 

@@

            F(x_{k + 1}) - F^* +

@@

                F(x_0) - F^* + \frac{\gamma_0}{2}\Vert v_k - x^*\Vert^2

@@

            The choice of $\rho_k \in (0, 1]$ is just a convenience for convergence analysis. 
            It's a belief that there exists sequence $\rho_k$ where $\rho_k \ge 1$ where the algorithm would have a chance at converging still. 

@@

\section{WAPG covers variants of APG in the literatures}
    Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} 
            &= \theta_t(z_{t + 1} - z_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            x_{t + 1} &= 
            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                x_t = (1 + \tau_t)y_t - \tau_t z_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            \\
            x_{t + 1} - z_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - z_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            z_{t + 1} - z_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - z_t
            \\
            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
        \end{align*}

@@

        \begin{proposition}[WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
            Suppose that $(y_i, x_i, v_i)$ are generated by 
            \hyperref[def:wapg]{Definition \ref*{def:wapg}}
            for all $0 \le i \le k$. 

@@

                L &\alpha_k^2 \le (1 - \alpha_k)L \alpha_{k - 1} + \mu \alpha_k. 
            \end{aligned}
            $$

@@

@@

        \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$ for all $0\le i \le k$ and $L\alpha_k^2\le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
            Let $(x_k, y_k, v_k)$ to be generated as specified by Definition \ref{def:wapg} by the $(\alpha_k)_{k \ge0}$.
            Then the iterate $(v_k)$ can be expressed without $y_k, v_k$: 
            $$
            \begin{aligned}
                y_k &= 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{aligned}
            $$
        \end{proposition}
        \begin{proof}
            From Proposition \ref{prop:wapg-intermediate-form}, set 
            \begin{align*}
                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
                \\
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
            To see, we have 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

    \begin{proposition}[WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
        Suppose any sequence $(\alpha_k)_{k \ge 0}$ satisfies recursively the conditions
        $L\alpha_k^2 \le (1 - \alpha_k)L\alpha_{k - 1}^2 + \alpha_k \mu$. 
        If $\alpha_k$ is used in the Similtar triangle form to generate the iterates $(x_k, y_k v_k)$. 
        Then the iterates are algebraically equivalent to: 
        $$
        \begin{aligned}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + ???(x_{k + 1} - x_k). 
        \end{aligned}
        $$
    \end{proposition}
    \begin{remark}

>>>>

\section{Stepwise formulation of weak accelerated proximal gradient}
    In this section, we introduce the following new quantities and their notations. 
    It's there to make the notations simpler and easier to follow for the proofs that will come later. 
    The algorithm is parameterized by the sequence $y_k, x_k$. 
    We define for all $k \ge 0$ the following quantities: 
    \begin{assumption}
        Choose any integer $k\ge 0$. 
        Given $x_k, y_k, v_k$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L y_k), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_Ly_k) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        Observe that by convexity of $F$, $\epsilon_k \ge 0$ always. 
    \end{assumption}

    \begin{theorem}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu \le L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$. 
        Define scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{theorem}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        With the equalities, we define the following quantities associate with it. 
        Fix any integer $k \ge 0$. 
        To verify, we use the fundamental proximal gradient inequality. 
        Next, observe that we have $x_k, y_k, v_k$ lie on the same line because they have 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\gamma_{k + 1}/\alpha_k \gamma_k$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma_k v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line.

@@

        But in general the choice of $\mu$ remains the strong convexity modulus or equivalently, any value that is smallar than the true strong convexity constant for claiming the convergence rate for all initial guesses. 

@@

\section{Formulation of R-WAPG and its convergence rates}

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_0 >= 0$, $(x_0, v_0)$ or equivalently $(x_0, y_0), (y_0, v_0)$. 
        Given any sequence $(\rho_k)_{k\ge0}, (\alpha_k)_{k \ge0}$ such that for all integer $k\ge 0$, $\textcolor{red}{\rho_k \ge 0}$, $\alpha_k \in (0, 1)$. 
        The algorithm generates a sequence of $(x_k, y_k, v_k)$ such that they satisfy for all $k\ge 0$ recursively: 
        \begin{align*}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 1,
                \\
                \gamma_0 & k = 0. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
    \end{observation}

    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
        Let vectors $(x_k, y_k, v_k)_{k \ge0}$ and scalars $\alpha_k$ be generated by R-WAPG. 

@@

@@

@@

        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2, \hat \gamma = L \alpha_k^2$, giving us: 

@@

            &F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

                F(x_k) - F^* + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2
            \max(1, \rho_{k - 1})(1 - \alpha_k)

@@

                \prod_{i = 0}^{k} \max(1, \rho_{k - 1})

@@

@@

            & F(x_{k + 1}) - F^* +

@@

@@

            The choice of $\rho_k$ allows for divergence to traditional choices of step sizes in the literatures. 
            As we can see from the above convergence claim, there exists choices of $\rho_k\ge 1$ where convergence remains possible. 

@@

\section{R-WAPG covers variants of APG in the literatures}
    Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} 
            &= \theta_t(z_{t + 1} - z_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            x_{t + 1} &= 
            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                x_t = (1 + \tau_t)y_t - \tau_t z_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            \\
            x_{t + 1} - z_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - z_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            z_{t + 1} - z_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - z_t
            \\
            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
        \end{align*}
    \end{proof}

@@

        \begin{proposition}[R-WAPG intermediate Form I]\label{prop:wapg-intermediate-form}
            Assume $\mu < L$. 
            Suppose that $(y_i, x_i, v_i)$ are generated by the WAPG algorithm for all $0 \le i \le k$ using sequence $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge0}$ such that for any integer $k\ge 0$, $\alpha_k \in (0, 1)$ and $\rho_k \ge 0$. 

@@

                L &\alpha_k^2 = (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 + \mu \alpha_k. 

@@

            On the third $\iff$, we can assume $\alpha_k \neq \mu/L$ because $\alpha_k = \mu/L$ is impossible. 
            For contradiction, assume $a_k = \mu/L$. 
            Then
                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
            Which contradict $\alpha_{k - 1} \in (0, 1)$. 

@@

        \begin{proposition}[WAPG fits similar triangle form]\label{prop:wagp-st-form}
            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.  
            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 
            \begin{align*}
                y_k &= 
                \left(
                    1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proposition}
        \begin{proof}
            From Proposition \ref{prop:wapg-intermediate-form}, set 
            \begin{align*}
                \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}, 
                \\
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (1 + \xi_k)^{-1}\delta_k &= \frac{1}{L\alpha_k}
                \iff L \delta_k = \frac{1 + \xi_k}{\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            Hence $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)$. 
            To see, we have 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}
